Decentralized autonomous organization to automate governance\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-04-07 paper/Paper.tex
update contracts

\subsection{DAO} \label{DAO}
\begin{verbatim}
contract DAOInterface {
    Proposal[] public proposals;
    uint minQuorumDivisor;
    uint lastTimeMinQuorumMet;
    uint public rewards;
    address[] public allowedRecipients;
    mapping (address => uint) public rewardToken;
    uint public totalRewardToken;
    ManagedAccount public rewardAccount;
    mapping (address => uint) public paidOut;
    mapping (address => uint) public blocked;
    uint public proposalDeposit;
    DAO_Creator public daoCreator;

@@

    function DAO(
        address _defaultServiceProvider,
        DAO_Creator _daoCreator,
        uint _minValue,
        uint _closingTime,
        address _privateSale
    )
    function () returns (bool success);
    function payDAO() returns(bool);
    function receiveEther() returns(bool);
    function newProposal(
        address _recipient,
        uint _amount,
        string _description,
        bytes _transactionData,
        uint _debatingPeriod,
        bool _newServiceProvider
    ) onlyTokenholders returns (uint _proposalID);
    function checkProposalCode(
        uint _proposalID,
        address _recipient,
        uint _amount,
        bytes _transactionData
    ) constant returns (bool _codeChecksOut);
    function vote(
        uint _proposalID,
        bool _supportsProposal
    ) onlyTokenholders returns (uint _voteID);
    function executeProposal(
        uint _proposalID,
        bytes _transactionData
    ) returns (bool _success);
    function splitDAO(
        uint _proposalID,
        address _newServiceProvider
    ) returns (bool _success);
    function addAllowedAddress(address _recipient) external returns (bool _success);
    function changeProposalDeposit(uint _proposalDeposit) external;
    function getMyReward() returns(bool _success);
    function withdrawRewardFor(address _account) returns(bool _success);
    function transferWithoutReward(address _to, uint256 _amount) returns (bool success);
    function transferFromWithoutReward(
        address _from,
        address _to,
        uint256 _amount
    ) returns (bool success);
    function halveMinQuorum() returns (bool _success);
    function numberOfProposals() constant returns (uint _numberOfProposals);
    function isBlocked(address _account) returns (bool);

@@

    // Proposals to spend the DAO's ether or to choose a new service provider
    Proposal[] public proposals;
    // The quorum needed for each proposal is partially calculated by
    // totalSupply / minQuorumDivisor
    uint minQuorumDivisor;
    // The unix time of the last time quorum was reached on a proposal
    uint lastTimeMinQuorumMet;
    // The total amount of wei received as reward that has not been sent to
    // the rewardAccount
    uint public rewards;
    // Address of the service provider
    address public serviceProvider;
    // The whitelist: List of addresses the DAO is allowed to send money to
    address[] public allowedRecipients;

@@

    // The account used to manage the rewards which are to be distributed to the
    // DAO Token Holders of any DAO that holds Reward Tokens
    ManagedAccount public rewardAccount;
    // Amount of rewards (in wei) already paid out to a certain address
    mapping (address => uint) public paidOut;
    // Map of addresses blocked during a vote (not allowed to transfer DAO
    // tokens). The address points to the proposal ID.
    mapping (address => uint) public blocked;

@@

    // A proposal with `newServiceProvider == false` represents a transaction
    // to be issued by this DAO
    // A proposal with `newServiceProvider == true` represents a DAO split
    struct Proposal {
        // The address where the `amount` will go to if the proposal is accepted
        // or if `newServiceProvider` is true, the proposed service provider of
        //the new DAO).
        address recipient;
        // The amount to transfer to `recipient` if the proposal is accepted.
        uint amount;
        // A plain text description of the proposal
        string description;
        // A unix timestamp, denoting the end of the voting period
        uint votingDeadline;
        // True if the proposal's votes have yet to be counted, otherwise False
        bool open;
        // True if quorum has been reached, the votes have been counted, and
        // the majority said yes
        bool proposalPassed;
        // A hash to check validity of a proposal
        bytes32 proposalHash;
        // Deposit in wei the creator added when submitting their proposal. It
        // is taken from the msg.value of a newProposal call.
        uint proposalDeposit;
        // True if this proposal is to assign a new service provider
        bool newServiceProvider;
        // Data needed for splitting the DAO
        SplitData[] splitData;
        // Number of tokens in favour of the proposal
        uint yea;
        // Number of tokens opposed to the proposal
        uint nay;
        // Simple mapping to check if a shareholder has voted for it
        mapping (address => bool) votedYes;
        // Simple mapping to check if a shareholder has voted against it
        mapping (address => bool) votedNo;
        // Address of the shareholder who created the proposal
        address creator;
    }

    // Used only in the case of a newServiceProvider porposal.
    struct SplitData {
        // The balance of the current DAO minus the deposit at the time of split
        uint splitBalance;
        // The total amount of DAO Tokens in existence at the time of split.
        uint totalSupply;
        // Amount of Reward Tokens owned by the DAO at the time of split.
        uint rewardToken;
        // The new DAO contract created at the time of split.
        DAO newDAO;
    }
    // Used to restrict acces to certain functions to only DAO Token Holders
    modifier onlyTokenholders {}

    /// @dev Constructor setting the default service provider and the address
    /// for the contract able to create another DAO as well as the parameters
    /// for the DAO Token Sale
    /// @param _defaultServiceProvider The default service provider
    /// @param _daoCreator The contract able to (re)create this DAO
    /// @param _minValue Minimal value for a successful DAO Token Sale
    /// @param _closingTime Date (in unix time) of the end of the DAO Token Sale
    /// @param _privateSale If zero the DAO Token Sale is open to public, a
    /// non-zero address means that the DAO Token Sale is only for the address
    // This is the constructor: it can not be overloaded so it is commented out
    //  function DAO(
        //  address _defaultServiceProvider,
        //  DAO_Creator _daoCreator,
        //  uint _minValue,
        //  uint _closingTime,
        //  address _privateSale
    //  )

    /// @notice Buy Token with `msg.sender` as the beneficiary
    function () returns (bool success);

    /// @dev Function used by the products of the DAO (e.g. Slocks) to send
    /// rewards to the DAO
    /// @return Whether the call to this function was successful or not
    function payDAO() returns(bool);

@@

    /// @notice `msg.sender` creates a proposal to send `_amount` Wei to
    ///  `_recipient` with the transaction data `_transactionData`. If
    /// `_newServiceProvider` is true, then this is a proposal that splits the
    /// DAO and sets `_recipient` as the new DAO's new service provider.
    /// @param _recipient Address of the recipient of the proposed transaction
    /// @param _amount Amount of wei to be sent with the proposed transaction
    /// @param _description String describing the proposal
    /// @param _transactionData Data of the proposed transaction
    /// @param _debatingPeriod Time used for debating a proposal, at least 2
    /// weeks for a regular proposal, 10 days for new service provider proposal
    /// @param _newServiceProvider Bool defining whether this proposal is about
    /// a new service provider or not
    /// @return The proposal ID. Needed for voting on the proposal
    function newProposal(
        address _recipient,
        uint _amount,
        string _description,
        bytes _transactionData,
        uint _debatingPeriod,
        bool _newServiceProvider
    ) onlyTokenholders returns (uint _proposalID);

@@

    /// @notice ATTENTION! I confirm to move my remaining funds to a new DAO
    /// with `_newServiceProvider` as the new service provider, as has been
    /// proposed in proposal `_proposalID`. This will burn my tokens. This can
    /// not be undone and will split the DAO into two DAO's, with two
    /// different underlying tokens.
    /// @param _proposalID The proposal ID
    /// @param _newServiceProvider The new service provider of the new DAO
    /// @dev This function, when called for the first time for this proposal,
    /// will create a new DAO and send the sender's portion of the remaining
    /// ether and Reward Tokens to the new DAO. It will also burn the DAO Tokens
    /// of the sender. 
    function splitDAO(
        uint _proposalID,
        address _newServiceProvider
    ) returns (bool _success);

@@

@@

    /// @notice Withdraw `account`'s portion of the reward from `rewardAccount`,
    /// to `account`'s balance
    /// @return Whether the call was successful
    function withdrawRewardFor(address _account) returns(bool _success);

@@

    function DAO(
        address _defaultServiceProvider,
        DAO_Creator _daoCreator,
        uint _minValue,
        uint _closingTime,
        address _privateSale
    ) TokenSale(_minValue, _closingTime, _privateSale) {

        serviceProvider = _defaultServiceProvider;
        daoCreator = _daoCreator;
        proposalDeposit = 20 ether;
        rewardAccount = new ManagedAccount(address(this));
        lastTimeMinQuorumMet = now;
        minQuorumDivisor = 5; // sets the minimal quorum to 20%
        proposals.length++; // avoids a proposal with ID 0 because it is used
        if (address(rewardAccount) == 0)
            throw;
    }

@@

    function payDAO() returns (bool) {
        rewards += msg.value;
        return true;
    }

@@

        if (_recipient == address(rewardAccount) && _amount > rewards)
            throw;

@@

        // Execute result
        if (quorum >= minQuorum(p.amount) && p.yea > p.nay) {
            if (!p.creator.send(p.proposalDeposit))
                throw;
            // Without this throw, the creator of the proposal can repeat this,
            // and get so much ether
            if (!p.recipient.call.value(p.amount)(_transactionData))
                throw;
            p.proposalPassed = true;
            _success = true;
            lastTimeMinQuorumMet = now;
            if (p.recipient == address(rewardAccount)) {
                // This happens when multiple similar proposals are created and
                // both are passed at the same time.
                if (rewards < p.amount)
                    throw;
                rewards -= p.amount;
            } else {
                rewardToken[address(this)] += p.amount;
                totalRewardToken += p.amount;
            }
        } else if (quorum >= minQuorum(p.amount) && p.nay >= p.yea) {
            if (!p.creator.send(p.proposalDeposit))
                throw;
            lastTimeMinQuorumMet = now;
        }

@@

        // Burn DAO Tokens
        Transfer(msg.sender, 0, balances[msg.sender]);
        totalSupply -= balances[msg.sender];
        balances[msg.sender] = 0;
        paidOut[address(p.splitData[0].newDAO)] += paidOut[msg.sender];
        paidOut[msg.sender] = 0;

@@

@@

    function withdrawRewardFor(address _account) noEther returns (bool _success) {
        // The account's portion of Reward Tokens of this DAO
        uint portionOfTheReward =
            (balanceOf(_account) * rewardToken[address(this)]) /
            totalSupply + rewardToken[_account];
        uint reward =
            (portionOfTheReward * rewardAccount.accumulatedInput()) /
            totalRewardToken - paidOut[_account];
        if (!rewardAccount.payOut(_account, reward))
            throw;
        paidOut[_account] += reward;
        return true;
    }

@@

    function addAllowedAddress(address _recipient) noEther external returns (bool _success) {
        if (msg.sender != serviceProvider)
            throw;
        allowedRecipients.push(_recipient);
        return true;
    }

    function isRecipientAllowed(address _recipient) internal returns (bool _isAllowed) {
        if (_recipient == serviceProvider
            || _recipient == address(rewardAccount)
            || _recipient == address(this)
            || (_recipient == address(extraBalance)
                // only allowed when at least the amount held in the
                // extraBalance account has been spent from the DAO
                && totalRewardToken > extraBalance.accumulatedInput()))
            return true;

        for (uint i = 0; i < allowedRecipients.length; ++i) {
            if (_recipient == allowedRecipients[i])
                return true;
        }
        return false;
    }

    function minQuorum(uint _value) internal returns (uint _minQuorum) {
        // minimum of 20% and maximum of 53.33%
        return totalSupply / minQuorumDivisor + _value / 3;
    }

@@

    function createNewDAO(address _newServiceProvider) internal returns (DAO _newDAO) {
        NewServiceProvider(_newServiceProvider);
        return daoCreator.createDAO(_newServiceProvider, 0, now + 42 days);
    }

@@

contract DAO_Creator {
    function createDAO(
        address _defaultServiceProvider,
        uint _minValue,
        uint _closingTime
    ) returns (DAO _newDAO) {

        return new DAO(
            _defaultServiceProvider,
            DAO_Creator(this),
            _minValue,
            _closingTime,
            msg.sender
        );
    }
}
\end{verbatim}

@@

    function setRewardDivisor(uint _rewardDivisor) callingRestriction {
        if (_rewardDivisor < 50 && msg.sender != address(client))
            throw; // 2% is the default max reward
        rewardDivisor = _rewardDivisor;
    }

    function setDeploymentFee(uint _deploymentReward) callingRestriction {
        if (deploymentReward > 10 ether && msg.sender != address(client))
            throw; 
        deploymentReward = _deploymentReward;
    }

    // interface for Slocks
    function payOneTimeReward() returns(bool) {
        if (msg.value < deploymentReward)
            throw;
        if (promiseValid) {
            if (client.payDAO.value(msg.value)()) {
                return true;
            } else {
                throw;
            }
        } else {
            if (serviceProvider.send(msg.value)) {
                return true;
            } else {
                throw;
            }
        }
    }

    // pay reward
    function payReward() returns(bool) {
        if (promiseValid) {
            if (client.payDAO.value(msg.value)()) {
                return true;
            } else {
                throw;
            }
        } else {
            if (serviceProvider.send(msg.value)) {
                return true;
            } else {
                throw;
            }
        }
    }
}
\end{verbatim}

>>>>

\subsection{DAO} \label{DAO}
\begin{verbatim}
contract DAOInterface {
    Proposal[] public proposals;
    uint minQuorumDivisor;
    uint lastTimeMinQuorumMet;
    address public serviceProvider;
    address[] public allowedRecipients;
    mapping (address => uint) public rewardToken;
    uint public totalRewardToken;
    ManagedAccount public rewardAccount;
    ManagedAccount public DAOrewardAccount;
    mapping (address => uint) public paidOut;
    mapping (address => uint) public DAOpaidOut;
    mapping (address => uint) public blocked;
    uint public proposalDeposit;
    DAO_Creator public daoCreator;

@@

    function DAO(
        address _defaultServiceProvider,
        DAO_Creator _daoCreator,
        uint _proposalDeposit,
        uint _minValue,
        uint _closingTime,
        address _privateSale
    )
    function () returns (bool success);
    function receiveEther() returns(bool);
    function newProposal(
        address _recipient,
        uint _amount,
        string _description,
        bytes _transactionData,
        uint _debatingPeriod,
        bool _newServiceProvider
    ) onlyTokenholders returns (uint _proposalID);
    function checkProposalCode(
        uint _proposalID,
        address _recipient,
        uint _amount,
        bytes _transactionData
    ) constant returns (bool _codeChecksOut);
    function vote(
        uint _proposalID,
        bool _supportsProposal
    ) onlyTokenholders returns (uint _voteID);
    function executeProposal(
        uint _proposalID,
        bytes _transactionData
    ) returns (bool _success);
    function splitDAO(
        uint _proposalID,
        address _newServiceProvider
    ) returns (bool _success);
    function newContract(address _newContract);
    function addAllowedAddress(address _recipient) external returns (bool _success);
    function changeProposalDeposit(uint _proposalDeposit) external;
    function retrieveDAOReward(bool _toMembers) external returns (bool _success);
    function getMyReward() returns(bool _success);
    function withdrawRewardFor(address _account) returns(bool _success);
    function transferWithoutReward(address _to, uint256 _amount) returns (bool success);
    function transferFromWithoutReward(
        address _from,
        address _to,
        uint256 _amount
    ) returns (bool success);
    function halveMinQuorum() returns (bool _success);
    function numberOfProposals() constant returns (uint _numberOfProposals);
    function isBlocked(address _account) returns (bool);

@@

    // Proposals to spend the DAO's ether or to choose a new service provider
    Proposal[] public proposals;
    // The quorum needed for each proposal is partially calculated by
    // totalSupply / minQuorumDivisor
    uint minQuorumDivisor;
    // The unix time of the last time quorum was reached on a proposal
    uint lastTimeMinQuorumMet;

    // Address of the service provider
    address public serviceProvider;
    // The whitelist: List of addresses the DAO is allowed to send money to
    mapping (address => bool) public allowedRecipients;

@@

    // The account used to manage the rewards which are to be distributed to the
    // DAO Token Holders of this DAO
    ManagedAccount public rewardAccount;

    // The account used to manage the rewards which are to be distributed to
    // any DAO that holds Reward Tokens
    ManagedAccount public DAOrewardAccount;

    // Amount of rewards (in wei) already paid out to a certain DAO
    mapping (address => uint) public DAOpaidOut;

    // Amount of rewards (in wei) already paid out to a certain address
    mapping (address => uint) public paidOut;
    // Map of addresses blocked during a vote (not allowed to transfer DAO
    // tokens). The address points to the proposal ID.
    mapping (address => uint) public blocked;

@@

    // A proposal with `newServiceProvider == false` represents a transaction
    // to be issued by this DAO
    // A proposal with `newServiceProvider == true` represents a DAO split
    struct Proposal {
        // The address where the `amount` will go to if the proposal is accepted
        // or if `newServiceProvider` is true, the proposed service provider of
        // the new DAO).
        address recipient;
        // The amount to transfer to `recipient` if the proposal is accepted.
        uint amount;
        // A plain text description of the proposal
        string description;
        // A unix timestamp, denoting the end of the voting period
        uint votingDeadline;
        // True if the proposal's votes have yet to be counted, otherwise False
        bool open;
        // True if quorum has been reached, the votes have been counted, and
        // the majority said yes
        bool proposalPassed;
        // A hash to check validity of a proposal
        bytes32 proposalHash;
        // Deposit in wei the creator added when submitting their proposal. It
        // is taken from the msg.value of a newProposal call.
        uint proposalDeposit;
        // True if this proposal is to assign a new service provider
        bool newServiceProvider;
        // Data needed for splitting the DAO
        SplitData[] splitData;
        // Number of Tokens in favour of the proposal
        uint yea;
        // Number of Tokens opposed to the proposal
        uint nay;
        // Simple mapping to check if a shareholder has voted for it
        mapping (address => bool) votedYes;
        // Simple mapping to check if a shareholder has voted against it
        mapping (address => bool) votedNo;
        // Address of the shareholder who created the proposal
        address creator;
    }

    // Used only in the case of a newServiceProvider porposal.
    struct SplitData {
        // The balance of the current DAO minus the deposit at the time of split
        uint splitBalance;
        // The total amount of DAO Tokens in existence at the time of split.
        uint totalSupply;
        // Amount of Reward Tokens owned by the DAO at the time of split.
        uint rewardToken;
        // The new DAO contract created at the time of split.
        DAO newDAO;
    }

    // Used to restrict access to certain functions to only DAO Token Holders
    modifier onlyTokenholders {}

    /// @dev Constructor setting the default service provider and the address
    /// for the contract able to create another DAO as well as the parameters
    /// for the DAO Token Sale
    /// @param _defaultServiceProvider The default service provider
    /// @param _daoCreator The contract able to (re)create this DAO
    /// @param _proposalDeposit The deposit to be paid for a regular proposal
    /// @param _minValue Minimal value for a successful DAO Token Sale
    /// @param _closingTime Date (in unix time) of the end of the DAO Token Sale
    /// @param _privateSale If zero the DAO Token Sale is open to public, a
    /// non-zero address means that the DAO Token Sale is only for the address
    // This is the constructor: it can not be overloaded so it is commented out
    //  function DAO(
        //  address _defaultServiceProvider,
        //  DAO_Creator _daoCreator,
        //  uint _proposalDeposit,
        //  uint _minValue,
        //  uint _closingTime,
        //  address _privateSale
    //  );

    /// @notice Buy Token with `msg.sender` as the beneficiary
    /// @return Whether the purchase was successful
    function () returns (bool success);

@@

    /// @notice `msg.sender` creates a proposal to send `_amount` Wei to
    /// `_recipient` with the transaction data `_transactionData`. If
    /// `_newServiceProvider` is true, then this is a proposal that splits the
    /// DAO and sets `_recipient` as the new DAO's service provider.
    /// @param _recipient Address of the recipient of the proposed transaction
    /// @param _amount Amount of wei to be sent with the proposed transaction
    /// @param _description String describing the proposal
    /// @param _transactionData Data of the proposed transaction
    /// @param _debatingPeriod Time used for debating a proposal, at least 2
    /// weeks for a regular proposal, 10 days for new service provider proposal
    /// @param _newServiceProvider Bool defining whether this proposal is about
    /// a new service provider or not
    /// @return The proposal ID. Needed for voting on the proposal
    function newProposal(
        address _recipient,
        uint _amount,
        string _description,
        bytes _transactionData,
        uint _debatingPeriod,
        bool _newServiceProvider
    ) onlyTokenholders returns (uint _proposalID);

@@

    /// @notice ATTENTION! I confirm to move my remaining funds to a new DAO
    /// with `_newServiceProvider` as the new service provider, as has been
    /// proposed in proposal `_proposalID`. This will burn my tokens. This can
    /// not be undone and will split the DAO into two DAO's, with two
    /// different underlying tokens.
    /// @param _proposalID The proposal ID
    /// @param _newServiceProvider The new service provider of the new DAO
    /// @dev This function, when called for the first time for this proposal,
    /// will create a new DAO and send the sender's portion of the remaining
    /// ether and Reward Tokens to the new DAO. It will also burn the DAO Tokens
    /// of the sender. (TODO: document rewardTokens - done??)
    function splitDAO(
        uint _proposalID,
        address _newServiceProvider
    ) returns (bool _success);

    /// @dev can only be called by the DAO itself through a proposal
    /// updates the contract of the DAO by sending all funds and rewardTokens
    /// to the new DAO. The new DAO needs to be approved by the service provider
    /// @param _newContract the address of the new contract
    function newContract(address _newContract);

@@

    /// @notice Move rewards from the DAORewards managed account
    /// @param _toMembers If true rewards are move to the actual reward account
    ///                   for the DAO. If not then it's moved to the DAO itself
    /// @return Whether the call was successful
    function retrieveDAOReward(bool _toMembers) external returns (bool _success);

@@

    /// @notice Withdraw `_account`'s portion of the reward from `rewardAccount`
    /// to `_account`'s balance
    /// @return Whether the call was successful
    function withdrawRewardFor(address _account) internal returns (bool _success);

@@

    function DAO(
        address _defaultServiceProvider,
        DAO_Creator _daoCreator,
        uint _proposalDeposit,
        uint _minValue,
        uint _closingTime,
        address _privateSale
    ) TokenSale(_minValue, _closingTime, _privateSale) {

        serviceProvider = _defaultServiceProvider;
        daoCreator = _daoCreator;
        proposalDeposit = _proposalDeposit;
        rewardAccount = new ManagedAccount(address(this));
        DAOrewardAccount = new ManagedAccount(address(this));
        if (address(rewardAccount) == 0)
            throw;
        if (address(DAOrewardAccount) == 0)
            throw;
        lastTimeMinQuorumMet = now;
        minQuorumDivisor = 5; // sets the minimal quorum to 20%
        proposals.length++; // avoids a proposal with ID 0 because it is used

        allowedRecipients[address(this)] = true;
        allowedRecipients[serviceProvider] = true;
    }

@@

@@

@@

        // Execute result
        if (quorum >= minQuorum(p.amount) && p.yea > p.nay) {
            if (!p.creator.send(p.proposalDeposit))
                throw;
            // Without this throw, the creator of the proposal can repeat this,
            // and get so much ether
            if (!p.recipient.call.value(p.amount)(_transactionData))
                throw;
            p.proposalPassed = true;
            _success = true;
            lastTimeMinQuorumMet = now;
            rewardToken[address(this)] += p.amount;
            totalRewardToken += p.amount;
        } else if (quorum >= minQuorum(p.amount) && p.nay >= p.yea) {
            if (!p.creator.send(p.proposalDeposit))
                throw;
            lastTimeMinQuorumMet = now;
        }

@@

        // Burn DAO Tokens
        Transfer(msg.sender, 0, balances[msg.sender]);
        withdrawRewardFor(msg.sender); // be nice, and get his rewards
        totalSupply -= balances[msg.sender];
        balances[msg.sender] = 0;
        paidOut[address(p.splitData[0].newDAO)] += paidOut[msg.sender];
        paidOut[msg.sender] = 0;

@@

    function newContract(address _newContract){
        if (msg.sender != address(this) || !allowedRecipients[_newContract]) return;
        // move all funds
        _newContract.call.value(address(this).balance)();

        //move all reward tokens
        rewardToken[_newContract] += rewardToken[address(this)];
        rewardToken[address(this)] = 0;
    }

    function retrieveDAOReward(bool _toMembers) external noEther returns (bool _success) {
        DAO dao = DAO(msg.sender);
        uint reward =
            (rewardToken[msg.sender] * DAOrewardAccount.accumulatedInput()) /
            totalRewardToken - DAOpaidOut[msg.sender];
        if(_toMembers) {
            if (!DAOrewardAccount.payOut(dao.rewardAccount(), reward))
                throw;
            }
        else {
            if (!DAOrewardAccount.payOut(dao, reward))
                throw;
        }
        DAOpaidOut[msg.sender] += reward;
        return true;
    }

@@

    function withdrawRewardFor(address _account) noEther internal returns (bool _success) {
        uint reward =
            (balanceOf(_account) * rewardAccount.accumulatedInput()) / totalSupply - paidOut[_account];
        if (!rewardAccount.payOut(_account, reward))
            throw;
        paidOut[_account] += reward;
        return true;
    }

@@

    function addAllowedAddress(address _recipient) noEther external returns (bool _success) {
        if (msg.sender != serviceProvider)
            throw;
        allowedRecipients[_recipient] = true;
        return true;
    }

    function isRecipientAllowed(address _recipient) internal returns (bool _isAllowed) {
        if (allowedRecipients[_recipient]
            || (_recipient == address(extraBalance)
                // only allowed when at least the amount held in the
                // extraBalance account has been spent from the DAO
                && totalRewardToken > extraBalance.accumulatedInput()))
            return true;
        else
            return false;
    }

    function minQuorum(uint _value) internal constant returns (uint _minQuorum) {
        // minimum of 20% and maximum of 53.33%
        return totalSupply / minQuorumDivisor +
            (_value * totalSupply) / (3 * (this.balance + totalRewardToken));
    }

@@

    function createNewDAO(address _newServiceProvider) internal returns (DAO _newDAO) {
        NewServiceProvider(_newServiceProvider);
        return daoCreator.createDAO(_newServiceProvider, 0, 0, now + 42 days);
    }

@@

contract DAO_Creator {
    function createDAO(
        address _defaultServiceProvider,
        uint _proposalDeposit,
        uint _minValue,
        uint _closingTime
    ) returns (DAO _newDAO) {

        return new DAO(
            _defaultServiceProvider,
            DAO_Creator(this),
            _proposalDeposit,
            _minValue,
            _closingTime,
            msg.sender
        );
    }
}
\end{verbatim}

@@

    function setRewardDivisor(uint _rewardDivisor) callingRestriction {
        if (_rewardDivisor < 50)
            throw; // 2% is the default max reward
        rewardDivisor = _rewardDivisor;
    }

    function setDeploymentFee(uint _deploymentReward) callingRestriction {
        if (deploymentReward > 10 ether)
            throw; // TODO, set a max defined by service provider, or ideally oracle (set in euro)
        deploymentReward = _deploymentReward;
    }

    // interface for Slocks
    function payOneTimeReward() returns(bool) {
        if (msg.value < deploymentReward)
            throw;
        if (promiseValid) {
            if (client.DAOrewardAccount().call.value(msg.value)()) {
                return true;
            } else {
                throw;
            }
        } else {
            if (serviceProvider.send(msg.value)) {
                return true;
            } else {
                throw;
            }
        }
    }

    // pay reward
    function payReward() returns(bool) {
        if (promiseValid) {
            if (client.DAOrewardAccount().call.value(msg.value)()) {
                return true;
            } else {
                throw;
            }
        } else {
            if (serviceProvider.send(msg.value)) {
                return true;
            } else {
                throw;
            }
        }
    }
}
\end{verbatim}
